Balsa: A Compact Line Notation Based on SMILES

### 2022-09-14 manuscript.tex
Adds abstract. Closes #54

>>>>

\begin{abstract}
Despite its widespread use, Simplified Molecular Input Line Entry System (SMILES) remains underspecified. The lack of a detailed specification encourages improvisation by software developers, complicates data standardization efforts, and undermines extension development. To address these problems this work proposes Balsa, a language subset of SMILES. A formal, machine-readable grammar defines Balsa's syntax. Semantics are described at three levels of resolution: constitution; configuration; and conformation. To estimate the compatibility of Balsa strings with SMILES software, all differences between the two languages were identified. To the extent that the SMILES documentation is unambiguous, every difference was consistent with a language subset relationship.
\end{abstract}
